Statically Typed String Sanitation Inside a Python (Technical Report)

### 2014-12-16 sanitation-psp14/tr/strings_chapter.tex
about to merge.

\item \textbf{$s = \rstrcase{e_1}{e_2}{x,y.e_3}$}.
\todo{finish...}

@@

\begin{thm}[Preservation]
If $\emptyset \vdash \iota : \tau$ and $\iota \mapsto \iota'$ then $\emptyset \vdash \iota' : \tau$.
\end{thm}
\begin{proof}
\todo{Fill in if there's time. Otherwise there's nothing interesting going on.}
\end{proof}

>>>>

\item \textbf{$s = \strcase{e_1}{e_2}{x,y.e_3}$}.
\todo{finish...}

@@

\begin{trlem}[Substitution Lemma] \label{lem:psubst}
If $\theta, x : \tau \vdash \iota : \tau'$ and $\theta \vdash \iota' : \tau$
then $\theta \vdash [\iota' / x]\iota : \tau'$.
\end{trlem}

\begin{thm}[Preservation]
If $\emptyset \vdash \iota : \tau$ and $\iota \mapsto \iota'$ then $\emptyset \vdash \iota' : \tau$.
\end{thm}
\begin{proof}

The proof proceeds by induction of the derivations of $\emptyset \vdash \iota : \tau$
and $\iota \mapsto \iota'$.

We treat only the non-lambda fragment.

\item \textbf{Case SP-E-ConcatLeft}.
Suppose:
\begin{align*}
  \iota &= \concat{\iota_1}{\iota_2} \mapsto \concat{\iota_1'}{\iota_2} \\
  \emptyset &\vdash \iota : \str \\
  \iota &\mapsto \iota' 
\end{align*}

The only appliable typing rule is P-T-Concat, so $\emptyset \vdash \iota_1 : \str$
and $\emptyset \vdash \iota_2 : \str$ where $\tau = \str$. 
By induction, $\emptyset \vdash \iota_1' : \str$,
so $\emptyset \vdash \concat{\iota_1'}{\iota_2} : \str$.

\item \textbf{Case SP-E-ConcatRight}
\begin{align*}
  e &= \concat{e_1}{e_2} \mapsto \concat{e_1}{e_2'} \\
  \emptyset &\vdash e : \str \\
  \iota &\mapsto \iota' 
\end{align*}

The only appliable typing rule is P-T-Concat, so $\emptyset \vdash \iota_1 : \str$
and $\emptyset \vdash \iota_2 : \str$ where $\tau = \str$. 
By induction, $\emptyset \vdash \iota_1' : \str$,
so $\emptyset \vdash \concat{\iota_1'}{\iota_2} : \str$.
